Monitoring forest health using hyperspectral imagery: Does feature selection improve the performance of machine-learning techniques?

### 2021-12-17 docs/00-manuscripts/mdpi/submissions/submission1/submission-1/performance-best-per-learner.tex
add assets of all submissions

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{The overall best individual learner performance across any task and filter method for RF, SVM, XGBoost, Lasso and Ridge, sorted ascending by RMSE (p.p.) including the respective standard error (SE) of the cross-validation run.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR & SVM & Relief & 28.12 & 19.12 \\ 
  2 & NRI & Lasso-MBO & No Filter & 31.16 & 15.03 \\ 
  3 & NRI & Ridge-MBO & No Filter & 31.16 & 15.03 \\ 
  4 & HR & regr.featureless & No Filter & 31.16 & 15.03 \\ 
  5 & HR & RF & Relief & 31.25 & 14.96 \\ 
  6 & HR & XGBoost & Car & 34.07 & 13.57 \\ 
   \hline
\end{tabular}
}
\end{table}

>>>>

% latex table generated in R 4.0.4 by xtable 1.8-4 package
\begin{table}[ht!]
\centering
\caption{The overall best individual learner performance across any task and filter method for RF, SVM, XGBoost, Lasso and Ridge, sorted ascending by RMSE (p.p.) including the respective standard error (SE) of the cross-validation run.} 
\label{tab:best-learner-perf}
\scalebox{0.9}{
\begin{tabular}{rlllrr}
  \hline
 & Task & Model & Filter & RMSE & SE \\ 
  \hline
1 & HR & SVM & Relief & 28.12 & 19.12 \\ 
  2 & NRI & Lasso-MBO & No Filter & 31.16 & 15.03 \\ 
  3 & NRI & Ridge-MBO & No Filter & 31.16 & 15.03 \\ 
  4 & - & regr.featureless & No Filter & 31.16 & 15.03 \\ 
  5 & HR & RF & Relief & 31.25 & 14.96 \\ 
  6 & HR & XGBoost & Car & 34.07 & 13.57 \\ 
   \hline
\end{tabular}
}
\end{table}

### 2021-12-17 docs/00-manuscripts/mdpi/submissions/submission2/submission-2.tex
add assets of all submissions

There was also no clear pattern in the percentage of features selected based on hyperparameter tuning (\autoref{tab:tune-perc-sel-features}).
The specific performance value to benchmark against during tuning is defined by the internal surrogate learner of the MBO tuning method and can be any numeric value between 0 and 1 (interpreted as a\ percentage of available features) for the hyperparameter that controls the number of features.
% Nevertheless, considering SVM's relative success, the use of at least a few hundred features from the combined feature set appears to be beneficial, or at least not harmful when the model's built-in regularization is capable of dealing with the resulting high-dimensional situation.

>>>>

There was also no clear pattern in the percentage of features selected based on hyperparameter tuning (\autoref{tab:tune-perc-sel-features}).
The optimal value for the number of features (interpreted as a\ percentage of available features), which are selected from the ranked filter results, is determined by the internal surrogate learner of the MBO tuning method using the results from the previous tuning iterations.
Due to this iterative approach MBO is in some ways able to evaluate how well a learning algorithm plays together with a certain amount of selected features and is subsequently able to adjust the number of variables to an optimal value.
All in all, considering SVM's relative success, the use of at least a few hundred features from the combined feature set appears to be beneficial, or at least not harmful when the model's built-in regularization is capable of dealing with the resulting high-dimensional situation.
